Algebraic File Synchronization: Adequacy and Completeness

### 2016-01-03 2015/abstract.tex
Improved abstract

With distributed computing and mobile applications,
synchronizing divergent replicas of data is a more and more common problem.
We investigate an operation-based approach to filesystem synchronization
and further our theoretical understanding of this problem
by presenting rigorous algebraic proofs that the algorithms desribed for
update detection and reconciliation return working solutions
that cannot be improved on.

To do this, we present our filesystem model 
and a novel, symmetric set of filesystem commands
with higher information content,
which allow us to simplify our definition of conflicting updates
compared to our previous approach,
and to ensure that we propagate all updates that do not cause errors.
We also present a number of generally useful properties of sequences of commands
including introducing the concept of inverse sequences and conditional operation.

These results are essential in
determining the outcome of an
application implementing an algebraic approach to synchronization
and in ensuring that it is error-free,
and as a step towards building a more complete algebra
to describe updates to filesystems and other storage protocols.

>>>>

With distributed computing and mobile applications,
synchronizing divergening replicas of data structures is a more and more common problem.
We use algebraic methods to reason about filesystem operations, 
and introduce a simplified definition of conflicting updates.
We also define algorithms for update detection and reconciliation
and present rigorous proofs that they not only work as intended,
but also cannot be improved on.

To achieve this, we introduce a novel, symmetric set of filesystem commands
with higher information content,
which removes edge cases
and increases the predictive powers of our algebraic model.
We also present a number of generally useful classes and properties
of sequences of commands.

These results are often intuitive,
but providing exact proofs for them is far from trivial.
They contribute to our understanding of this special type of algebraic model,
and toward building a more complete algebra
of filesystems and other storage protocols.
They also form a theoretical basis for
specifying
and guaranteeing the error-free operation
of applications that implement operation-based approaches to synchronization.
